### 2014-03-15 src/analysis.Rnw
Fix space requirements

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

>>>>

\begin{table*}
\begin{minipage}[htb]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

### 2014-03-15 src/threats.Rnw
Fix space requirements

Our results were observed on open source Java programs from the Github repository, using the
maven build system. Further, only those projects that successfully completed mutation
testing within a designated amount of time were chosen. This implies that if there is a
confounding factor in play that affects the relation between the full mutation score and
sampling mutation score, and any of the noted factors, it might cause our results to be
either wrong or less applicable.

>>>>

Our results were observed on open source Java programs from the Github repository, using the
maven build system. Further, only those projects that successfully completed mutation
testing within a designated amount of time were chosen. This implies that if there is a
confounding factor in play that affects the relation between the full mutation score and
sampling mutation score, it might cause our results to be either wrong or less applicable.
